Pillar 2 - Topic Modeling

### 2019-05-07 Pillar 2 - Topic Modeling.Rmd
my_control

  mutate(
         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control

@@

#Input vectors
which_texts <- "catalogues"
topic_numbers <-seq(from = 5, to = 150, by = 5)

>>>>

  mutate(
         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control

@@

#Input vectors
which_texts <- "catalogues"
topic_numbers <-seq(from = 5, to = 200, by = 5)
